### 2014-10-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to title and metadata

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Basement Fire in a Wood Frame Residential Structure - San Francisco, CA},
  pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
  pdfsubject={Insert abstract here.},
  pdfkeywords={insert; keywords; here}
}

@@

\headerB{
Simulation of a Basement Fire \\
in a Wood Frame Residential \\
Structure - San Francisco, CA \\
}

@@

\headerB{
Simulation of a Basement Fire \\
in a Wood Frame Residential \\
Structure - San Francisco, CA \\
}

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Daniel Madrzykowski \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_First_Floor}
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
\caption{Summary of simulated flow path in the stairwell on the first floor and basement floor 120~s after the first rear basement window failure. The arrows indicate the direction of flow. Two arrows located at a door or window indicate bi-directional flow at a vent opening. The maximum velocity (red) corresponds to 9~m/s (20~mph).}
\label{fig:flow_path_top}
\end{figure}

>>>>

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Fire in a Hillside Residential Structure - San Francisco, CA},
  pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
  pdfsubject={The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters. The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions. The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area. The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell. The temperature of the gases in the interior stairwell was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F). Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure. After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided. The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.},
  pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
}

@@

\headerB{
Simulation of a Fire in a Hillside \\
Residential Structure - \\
San Francisco, CA \\
}

@@

\headerB{
Simulation of a Fire in a Hillside \\
Residential Structure - \\
San Francisco, CA \\
}

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Daniel Madrzykowski \\
{\em Fire Research Division \\
Engineering Laboratory \\

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_First_Floor}
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
\caption{Summary of simulated flow path in the stairwell on the first floor and basement floor 120~s after the first rear basement window failure. The arrows indicate the direction of flow. Two arrows located at a door or window indicate bi-directional flow at a vent opening. The maximum velocity is indicated by the red contour and corresponds to 9~m/s (20~mph).}
\label{fig:flow_path_top}
\end{figure}
